Through the eyes of the teacher

### 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
update paper supplement

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Informationand and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r table-all-scales-self-assessment, echo = FALSE}

@@

# format and insert table in manuscript
apa_table(
  teacher.scale.quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

@@

```{r table-all-scales-students, echo = FALSE}

@@

# format and insert table in manuscript
apa_table(
  student.scale.quest.table,
  caption = "Scale analysis for students' perspective",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

>>>>

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r table-all-scales-self-assessment, echo=FALSE, message=FALSE, warning=FALSE}

@@

# format and insert table in manuscript
apa_table(
  teacher.scale.quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

@@

```{r table-all-scales-students, echo=FALSE, message=FALSE, warning=FALSE}

@@

# format and insert table in manuscript
apa_table(
  student.scale.quest.table,
  caption = "Scale analysis for students' perspective",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

### 2021-03-03 paper_1/paper_1_supplement_new_table.tex
update paper supplement

\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}

@@

\begin{verbatim}
## Warning in alpha(self.cs.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

\begin{verbatim}
## Warning in sqrt(Vtc): NaNs wurden erzeugt
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in alpha(self.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

\begin{verbatim}
## Warning in sqrt(Vtc): NaNs wurden erzeugt
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in alpha(self.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

@@

@@

\begin{verbatim}
## Warning in alpha(stud.ppg.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

\begin{verbatim}
## Warning in alpha(stud.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

\begin{verbatim}
## Warning in alpha(stud.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

@@

>>>>

\caption{\label{tab:demographicspilottable}Demographic Information and Teaching Experience}

@@

@@

@@

@@

@@

\tiny{

@@

@@

@@

@@

\caption{\label{tab:Disturbance "head on table" to first intervention}Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention}

\begin{tabular}{lllllll}
\toprule
Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 3.00 & 2,079.00 & 693.00 & 5,735.00 & 231.00\\
01\_02\_A & Expert & 7.00 & 2,778.00 & 397.00 & 8,454.00 & 56.71\\
01\_03\_B & Novice & 1.00 & 460.00 & 460.00 & 3,493.00 & 460.00\\
01\_04\_C & Novice & 29.00 & 12,653.00 & 436.00 & 16,245.00 & 15.03\\
\bottomrule
\end{tabular}
